State Results

### 2023-07-18 reports/county_figures.Rmd
update manuscript & supplement

names(pal) <- c("Covidestim",
                '$P(S_1|untested)$ Centered at Survey Value',
                '$P(S_1|untested)$ and $\\beta$ Centered at Survey Values',
               "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
               "$\\beta$ Centered at Survey Value"
               )

@@

  if(to_newlines) {
    gsub("$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
         "$\\overset{Priors\\,Do\\,Not\\,Vary}{\\,by\\,State\\,and\\,Date}$", 
         as.character(labels),
         fixed=TRUE) %>%
    gsub("$P(S_1|untested)$ and $\\beta$ Centered at Survey Values",
         "$\\overset{P(S_1|untested)\\,and\\,beta}{Centered\\,at\\,Survey\\,Values}", 
         .,
         fixed=TRUE)
  }
  else {
      gsub(
         "$\\overset{Priors\\,Do\\,Not\\,Vary}{\\,by\\,State\\,and\\,Date}$", 
         "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
         as.character(labels),
         fixed=TRUE) %>%
    gsub("$\\overset{P(S_1|untested)\\,and\\,beta}{Centered\\,at\\,Survey\\,Values}",
         "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values",
         .,
         fixed=TRUE)
  }

@@

versions <- tibble(
  version = c("v1", "v2", "v3", "v4", "v5", "v6", "v7"),
  vlabel = factor(
    c( "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
    "$\\beta$ Centered at Survey Value",
    "$P(S_1|untested)$ Centered at Survey Value",
    "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values",
        "$\\beta$ Centered at Survey Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$"
    ),
    levels = c(
        "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
        "$\\beta$ Centered at Survey Value",
         "$P(S_1|untested)$ Centered at Survey Value",
        "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values",
        "$\\beta$ Centered at Survey Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$"

@@

  county <- county %>%
    left_join(versions) %>%
    mutate(vlabel=case_when(
      version == "v7" ~  "$\\overset{Priors\\,Do\\,Not\\,Vary}{\\,by\\,State\\,and\\,Date}$",
      version == "v5" ~ "$\\beta$ Centered at Survey Value",
      version =="v6" ~  "$\\overset{P(S_1|untested)\\,and\\,beta}{Centered\\,at\\,Survey\\,Values}",
      version == "v3" ~ "$P(S_1|untested)$ Centered at Survey Value",
    )) %>%
    mutate(vlabel =factor(vlabel,levels= c(
        "$\\overset{Priors\\,Do\\,Not\\,Vary}{\\,by\\,State\\,and\\,Date}$", 
         "$P(S_1|untested)$ Centered at Survey Value",
         "$\\beta$ Centered at Survey Value",
        "$\\overset{P(S_1|untested)\\,and\\,beta}{Centered\\,at\\,Survey\\,Values}"))) %>%
    left_join(county_names) %>%
    mutate(name = ifelse(fips =="25007,25019", "Nantucket and Dukes", name)) %>%
    left_join(dates,  relationship = "many-to-many") %>%
    group_by(biweek) %>%
    mutate(mindate = min(date),
           maxdate = max(date)) %>%
    ungroup()

@@

  wjoined <- wjoined %>%
    mutate(vlabel=case_when(
      version == "v7" ~  "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
      version == "v5" ~ "$\\beta$ Centered at Survey Value",
      version =="v6" ~  "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values",
      version == "v3" ~ "$P(S_1|untested)$ Centered at Survey Value"
    ))

@@

names(pal) <- c(#"$observed$", 
                '$P(S_1|untested)$ Centered at Survey Value',
                "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values",
               "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
               "$\\beta$ Centered at Survey Value"
               )

@@

names(pal) <- c(#"$observed$", 
                '$P(S_1|untested)$ Centered at Survey Value',
                '$P(S_1|untested)$ and $\\beta$ Centered at Survey Values',
               "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
               "$\\beta$ Centered at Survey Value"
               )

@@

##############################################
# stacked bar chart of concordance by county
##############################################
ma_concordance_by_county %>%
  filter(vlabel=="$P(S_1|untested)$ Centered at Survey Value") %>%
  group_by(name) %>%
  mutate(m = prop[which(in_interval=="In Interval")]) %>%
  ungroup() %>%
  mutate(in_interval = factor(in_interval, levels = c("Above Interval",
                            "In Interval", "Below Interval"))) %>%
  ggplot(aes(x= fct_reorder(name,m), 
             fill = (in_interval), y =prop)) + 
  geom_bar(stat="identity",position="stack") +
  theme_c() +
  coord_flip()+
  scale_fill_manual(values=c("In Interval" = "#79D2AF",
                             "Above Interval" = "#D2AF79",
                      "Below Interval"="#7997D2")) +
  labs(x="", 
       y= "Proportion",
       fill = "Covidestim Median:",
       title = "Massachusetts: Proportion Where Covidestim Median\nWas Within, Above, or Below the Median",
       subtitle = TeX("For Implementation with $P(S_1|untested)$ Centered at Survey Value")) +
  theme_c() +
  theme(legend.position="right",
          legend.title = element_text(face="bold", size = 15),
          legend.text= element_text( size = 15),
          legend.spacing.y = unit(3, 'pt'),
          axis.text.y = element_text(size = 17, hjust=1))

@@

county %>% 
  mutate(name=gsub("Nantucket and Dukes", "Nantucket\nand Dukes", name)) %>%
  mutate(vlabel=fct_reorder(vlabel,as.numeric(vlabel),.desc=TRUE)) %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill = vlabel),
             alpha = .7,
             show.legend=FALSE) +
  facet_grid(name~vlabel, 
             labeller=labeller(vlabel =as_labeller(
               TeX, default=label_parsed)),
             scales="free") +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
          legend.position = "top",
          strip.text.x=element_text(size=13,color='white'),
              axis.title = element_text(size=17),
          plot.title = element_text(size=24, hjust = .5, face="bold", 
                                    margin=margin(2,0,2,0)),
          plot.subtitle = element_text(size=20, face="italic",
                                       margin=margin(1,0,5,0))) +
  scale_fill_manual(values = pal)  +
  labs(x="",
       y = "Estimated Infections",
       title = "Simulation Intervals Over Time",
       subtitle = "Counties in Massachusetts")

@@

@@

county_relab <- county %>%
  mutate(vlabel=case_when(
      version == "v7" ~  "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
      version == "v5" ~ "$\\beta$ Centered at Survey Value",
      version =="v6" ~  "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values",
      version == "v3" ~ "$P(S_1|untested)$ Centered at Survey Value",
    )) %>%
    mutate(vlabel =factor(vlabel,levels= c(
        "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
         "$P(S_1|untested)$ Centered at Survey Value",
         "$\\beta$ Centered at Survey Value",
       "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values"))) %>%
    mutate(vlabel=fct_reorder(vlabel,as.numeric(vlabel),.desc=TRUE)) %>%
  filter(biweek>=6)

@@

@@

versions <- tibble(
  version = c( "v3", "v5", "v6", "v7"),
  vlabel = factor(
    c(  "$P(S_1|$untested) Centered at Survey Value"  ,
    "$\\beta$ Centered at Survey Value",
    "$P(S_1|$untested) and $\\beta$ Centered at Survey Values",
     "Priors Do Not Vary by State or Date"
    ),
    levels =   c(  "$P(S_1|$untested) Centered at Survey Value"  ,
    "$\\beta$ Centered at Survey Value",
    "$P(S_1|$untested) and $\\beta$ Centered at Survey Values",
     "Priors Do Not Vary by State or Date"
    ))
)
```

>>>>

names(pal) <- c("Covidestim",
                '$Pr(S_1|untested)$ Centered at Survey Value',
                '$Pr(S_1|untested)$ and $\\beta$ Centered at Survey Values',
               "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
               "$\\beta$ Centered at Survey Value"
               )

@@

  if(to_newlines) {
    gsub("$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
         "$\\overset{Priors\\,Do\\,Not\\,Vary}{\\,by\\,State\\,and\\,Date}$", 
         as.character(labels),
         fixed=TRUE) %>%
    gsub("$Pr(S_1|untested)$ and $\\beta$ Centered at Survey Values",
         "$\\overset{Pr(S_1|untested)\\,and\\,beta}{Centered\\,at\\,Survey\\,Values}$", 
         .,
         fixed=TRUE)
  }
  else {
      gsub(
         "$\\overset{Priors\\,Do\\,Not\\,Vary}{\\,by\\,State\\,and\\,Date}$", 
         "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
         as.character(labels),
         fixed=TRUE) %>%
    gsub("$\\overset{Pr(S_1|untested)\\,and\\,beta}{Centered\\,at\\,Survey\\,Values}$",
         "$Pr(S_1|untested)$ and $\\beta$ Centered at Survey Values",
         .,
         fixed=TRUE)
  }

@@

versions <- tibble(
  version = c("v1", "v2", "v3", "v4", "v5", "v6", "v7"),
  vlabel = factor(
    c( "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
    "$\\beta$ Centered at Survey Value",
    "$Pr(S_1|untested)$ Centered at Survey Value",
    "$Pr(S_1|untested)$ and $\\beta$ Centered at Survey Values",
        "$\\beta$ Centered at Survey Value (Spline Smoothed)",
         "$Pr(S_1|untested)$ and $\\beta$ Centered at Survey Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$"
    ),
    levels = c(
        "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
        "$\\beta$ Centered at Survey Value",
         "$Pr(S_1|untested)$ Centered at Survey Value",
        "$Pr(S_1|untested)$ and $\\beta$ Centered at Survey Values",
        "$\\beta$ Centered at Survey Value (Spline Smoothed)",
         "$Pr(S_1|untested)$ and $\\beta$ Centered at Survey Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$"

@@

  county <- county %>%
    left_join(versions) %>%
    mutate(vlabel=case_when(
      version == "v7" ~  "$\\overset{Priors\\,Do\\,Not\\,Vary}{\\,by\\,State\\,and\\,Date}$",
      version == "v5" ~ "$\\beta$ Centered at Survey Value",
      version =="v6" ~  "$\\overset{Pr(S_1|untested)\\,and\\,beta}{Centered\\,at\\,Survey\\,Values}$",
      version == "v3" ~ "$Pr(S_1|untested)$ Centered at Survey Value",
    )) %>%
    mutate(vlabel =factor(vlabel,levels= c(
        "$\\overset{Priors\\,Do\\,Not\\,Vary}{\\,by\\,State\\,and\\,Date}$", 
         "$Pr(S_1|untested)$ Centered at Survey Value",
         "$\\beta$ Centered at Survey Value",
        "$\\overset{Pr(S_1|untested)\\,and\\,beta}{Centered\\,at\\,Survey\\,Values}$"))) %>%
    left_join(county_names) %>%
    mutate(name = ifelse(fips =="25007,25019", "Nantucket and Dukes", name)) %>%
    left_join(dates,  relationship = "many-to-many") %>%
    group_by(biweek) %>%
    mutate(mindate = min(date),
           maxdate = max(date)) %>%
    ungroup()

@@

  wjoined <- wjoined %>%
    mutate(vlabel=case_when(
      version == "v7" ~  "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
      version == "v5" ~ "$\\beta$ Centered at Survey Value",
      version =="v6" ~  "$Pr(S_1|untested)$ and $\\beta$ Centered at Survey Values",
      version == "v3" ~ "$Pr(S_1|untested)$ Centered at Survey Value"
    ))

@@

names(pal) <- c(#"$observed$", 
                '$Pr(S_1|untested)$ Centered at Survey Value',
                "$Pr(S_1|untested)$ and $\\beta$ Centered at Survey Values",
               "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
               "$\\beta$ Centered at Survey Value"
               )

@@

names(pal) <- c(#"$observed$", 
                '$Pr(S_1|untested)$ Centered at Survey Value',
                '$Pr(S_1|untested)$ and $\\beta$ Centered at Survey Values',
               "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
               "$\\beta$ Centered at Survey Value"
               )

@@

##############################################
# stacked bar chart of concordance by county
##############################################
ma_concordance_by_county %>%
  filter(vlabel=="$Pr(S_1|untested)$ Centered at Survey Value") %>%
  group_by(name) %>%
  mutate(m = prop[which(in_interval=="In Interval")]) %>%
  ungroup() %>%
  mutate(in_interval = factor(in_interval, levels = c("Above Interval",
                            "In Interval", "Below Interval"))) %>%
  ggplot(aes(x= fct_reorder(name,m), 
             fill = (in_interval), y =prop)) + 
  geom_bar(stat="identity",position="stack") +
  theme_c() +
  coord_flip()+
  scale_fill_manual(values=c("In Interval" = "#79D2AF",
                             "Above Interval" = "#D2AF79",
                      "Below Interval"="#7997D2")) +
  labs(x="", 
       y= "Proportion",
       fill = "Covidestim Median:",
       title = "Massachusetts: Proportion Where Covidestim Median\nWas Within, Above, or Below the Median",
       subtitle = TeX("For Implementation with $Pr(S_1|untested)$ Centered at Survey Value")) +
  theme_c() +
  theme(legend.position="right",
          legend.title = element_text(face="bold", size = 15),
          legend.text= element_text( size = 15),
          legend.spacing.y = unit(3, 'pt'),
          axis.text.y = element_text(size = 17, hjust=1))

@@

county %>% 
  # only include dates where there were estimates for all implementations 
  filter(biweek >=6) %>%
  mutate(name=gsub("Nantucket and Dukes", "Nantucket\nand Dukes", name)) %>%
  mutate(vlabel=fct_reorder(vlabel,as.numeric(vlabel),.desc=TRUE)) %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill = vlabel),
             alpha = .7,
             show.legend=FALSE) +
  facet_grid(name~vlabel, 
             labeller=labeller(vlabel =as_labeller(
               TeX, default=label_parsed)),
             scales="free") +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
          legend.position = "top",
          strip.text.x=element_text(size=13,color='white'),
              axis.title = element_text(size=17),
          plot.title = element_text(size=24, hjust = .5, face="bold", 
                                    margin=margin(2,0,2,0)),
          plot.subtitle = element_text(size=20, face="italic",
                                       margin=margin(1,0,5,0))) +
  scale_fill_manual(values = pal)  +
  labs(x="",
       y = "Estimated Infections",
       title = "Simulation Intervals Over Time",
       subtitle = "Counties in Massachusetts")

@@

```{r,results='asis'}

version_with_max <- function(variable) {
   county %>%
    mutate(vlabel = convert_labels(vlabel, to_newlines=FALSE)) %>%
    select(-date) %>%
    distinct() %>% 
    # only include biweeks where all implementations have estimates
    filter(biweek >=6) %>%
    group_by(biweek,fips) %>%
    slice_max(n=1,order_by=!!sym(variable), with_ties=FALSE) %>%
    group_by(vlabel) %>%
    summarize(n=n()) %>%
    ungroup() %>%
    mutate(total=sum(n),
           prop=n/total)
}

version_with_min <- function(variable) {
   county %>%
    mutate(vlabel = convert_labels(vlabel, to_newlines=FALSE)) %>%
    select(-date) %>%
    distinct() %>% 
    # only include biweeks where all implementations have estimates
    filter(biweek >=6) %>%
    group_by(biweek,  fips) %>%
    slice_min(n=1,order_by=!!sym(variable), with_ties=FALSE) %>%
    group_by(vlabel) %>%
    summarize(n=n()) %>%
    ungroup() %>%
    mutate(total=sum(n),
           prop=n/total) 
}

# 
# county %>%
#     select(-date) %>%
#     distinct() %>% 
#     # only include biweeks where all implementations have estimates
#     filter(biweek >=6) %>%
#     group_by(biweek,fips) %>%
#    # slice_min(n=1,order_by=!!sym(variable), with_ties=FALSE)  %>%
#   select(exp_cases_lb, biweek, fips,version) %>%
#   pivot_wider(values_from = exp_cases_lb, names_from=version ) %>%
#   mutate(diff=v3-v7) %>%
#   pull(diff) %>%
#   mean()

version_with_max_median <- version_with_max("exp_cases_median")
version_with_min_median <- version_with_min("exp_cases_median")

version_with_max_lb <- version_with_max("exp_cases_lb")
version_with_min_lb <- version_with_min("exp_cases_lb")

version_with_max_ub <- version_with_max("exp_cases_ub")
version_with_min_ub <- version_with_min("exp_cases_ub")

#############
# MEDIAN
#############
cat("* The implementatation that most frequently had the maximum median cases across the two-week intervals was",
    as.character(version_with_max_median$vlabel[which.max(version_with_max_median$prop)]), 
    "where the median of", 
    version_with_max_median$prop[which.max(version_with_max_median$prop)] *100 %>% round(3),
    "percent of simulation intervals was highest.")

cat("* The implementatation that most frequently had the minimum median cases across the two-week intervals was",
    as.character(version_with_min_median$vlabel[which.max(version_with_min_median$prop)]), 
    "where the median of", 
    version_with_min_median$prop[which.max(version_with_min_median$prop)] *100 %>% round(3),
    "percent of simulation intervals was lowest.")

#################
# LOWER QUANTILE
#################

cat("* The implementatation that most frequently had the maximum 2.7% percentile in infections across the two-week intervals was",
    as.character(version_with_max_lb$vlabel[which.max(version_with_max_lb$prop)]), 
    "where the median of", 
    version_with_max_lb$prop[which.max(version_with_max_lb$prop)] *100 %>% round(3),
    "percent of simulation intervals was highest.")

cat("* The implementatation that most frequently had the minimum 97.5% percentile in infections across the two-week intervals was",
    as.character(version_with_min_lb$vlabel[which.max(version_with_min_lb$prop)]), 
    "where the median of", 
    version_with_min_lb$prop[which.max(version_with_min_lb$prop)] *100 %>% round(3),
    "percent of simulation intervals was lowest.")

@@

county_relab <- county %>%
  mutate(vlabel=case_when(
      version == "v7" ~  "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
      version == "v5" ~ "$\\beta$ Centered at Survey Value",
      version =="v6" ~  "$Pr(S_1|untested)$ and $\\beta$ Centered at Survey Values",
      version == "v3" ~ "$Pr(S_1|untested)$ Centered at Survey Value",
    )) %>%
    mutate(vlabel =factor(vlabel,levels= c(
        "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
         "$Pr(S_1|untested)$ Centered at Survey Value",
         "$\\beta$ Centered at Survey Value",
       "$Pr(S_1|untested)$ and $\\beta$ Centered at Survey Values"))) %>%
    mutate(vlabel=fct_reorder(vlabel,as.numeric(vlabel),.desc=TRUE)) %>%
  filter(biweek>=6)

@@

# only two implementations included

versions_to_include <- c(version_with_max_median$vlabel[which.max(version_with_max_median$prop)],
                         version_with_min_median$vlabel[which.max(version_with_min_median$prop)]) %>%
  unlist() %>% as.character()

versions_to_include

# switch labels to version without line breaks for clearer legend
# names(pal) <- convert_labels(labels(pal), to_newlines=FALSE)
names(pal)

county_relab <- county %>%
  mutate(vlabel=convert_labels(vlabel, to_newlines=FALSE)) %>%
  filter(vlabel %in% versions_to_include) %>%
  mutate(vlabel=case_when(
      version == "v7" ~  "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
      version == "v5" ~ "$\\beta$ Centered at Survey Value",
      version =="v6" ~  "$Pr(S_1|untested)$ and $\\beta$ Centered at Survey Values",
      version == "v3" ~ "$Pr(S_1|untested)$ Centered at Survey Value",
    )) %>%
    mutate(vlabel =factor(vlabel,levels= c(
        "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
         "$Pr(S_1|untested)$ Centered at Survey Value",
         "$\\beta$ Centered at Survey Value",
       "$Pr(S_1|untested)$ and $\\beta$ Centered at Survey Values"))) %>%
    mutate(vlabel=fct_reorder(vlabel,as.numeric(vlabel),.desc=TRUE)) %>%
  filter(biweek>=6)

ggsave(here('figures/simulation-intervals-color-version-only-2-county.pdf'))

@@

versions <- tibble(
  version = c( "v3", "v5", "v6", "v7"),
  vlabel = factor(
    c(  "$Pr(S_1|$untested) Centered at Survey Value"  ,
    "$\\beta$ Centered at Survey Value",
    "$Pr(S_1|$untested) and $\\beta$ Centered at Survey Values",
     "Priors Do Not Vary by State or Date"
    ),
    levels =   c(  "$Pr(S_1|$untested) Centered at Survey Value"  ,
    "$\\beta$ Centered at Survey Value",
    "$Pr(S_1|$untested) and $\\beta$ Centered at Survey Values",
     "Priors Do Not Vary by State or Date"
    ))
)
```

### 2023-07-18 reports/state_figures.Rmd
update manuscript & supplement

# clear labels for versions
versions <- tibble(
  version = c("v1", "v2", "v3", "v4", "v5", "v6", "v7"),
  vlabel = factor(
    c( "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
    "$\\beta$ Centered at Survey Value",
    "$P(S_1|untested)$ Centered at Survey Value",
    "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values",
        "$\\beta$ Centered at Survey Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$"
    ),
    levels = c(
        "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
        "$\\beta$ Centered at Survey Value",
         "$P(S_1|untested)$ Centered at Survey Value",
        "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values",
        "$\\beta$ Centered at Survey Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$"
    ) )
)

@@

@@

if(filter_versions){
  state_res <- state_res %>%
  filter(version %in% c("v3", "v5", "v6", "v7"))  %>%
    mutate(vlabel=case_when(
      version == "v7" ~  "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
      version == "v5" ~ "$\\beta$ Centered at Survey Value",
      version =="v6" ~  "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values",
      version == "v3" ~ "$P(S_1|untested)$ Centered at Survey Value"
    ))

>>>>

# clear labels for versions
versions <- tibble(
  version = c("v1", "v2", "v3", "v4", "v5", "v6", "v7"),
  vlabel = factor(
    c( "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
    "$\\beta$ Centered at Survey Value",
    "$Pr(S_1|untested)$ Centered at Survey Value",
    "$Pr(S_1|untested)$ and $\\beta$ Centered at Survey Values",
        "$\\beta$ Centered at Survey Value (Spline Smoothed)",
         "$Pr(S_1|untested)$ and $\\beta$ Centered at Survey Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$"
    ),
    levels = c(
        "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
        "$\\beta$ Centered at Survey Value",
         "$Pr(S_1|untested)$ Centered at Survey Value",
        "$Pr(S_1|untested)$ and $\\beta$ Centered at Survey Values",
        "$\\beta$ Centered at Survey Value (Spline Smoothed)",
         "$Pr(S_1|untested)$ and $\\beta$ Centered at Survey Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$"
    ) )
)

@@

dates %>% 
  group_by(biweek) %>%
  summarize(mindate=min(date),maxdate=max(date))

@@

if(filter_versions){
  state_res <- state_res %>%
  filter(version %in% c("v3", "v5", "v6", "v7"))  %>%
    mutate(vlabel=case_when(
      version == "v7" ~  "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$",
      version == "v5" ~ "$\\beta$ Centered at Survey Value",
      version =="v6" ~  "$Pr(S_1|untested)$ and $\\beta$ Centered at Survey Values",
      version == "v3" ~ "$Pr(S_1|untested)$ Centered at Survey Value"
    ))
